---
title: "GP Cluster Profiles"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    css: phs_style.css
---

```{r setup, include=FALSE}
library(flexdashboard)
library(crosstalk)
library(tidyverse)
```

Information {data-icon="fa-info-circle"}
================================================================================

We could put some high level summaries on this page (e.g. biggest changes since last year, or biggest difference to HSCP - although note that for some clusters in Lothian they compare to HB since cluster is essentially just the HSCP).

Notes could either go on this page, or could go on a separate "Notes" Page.

<!-- Cluster Level Tabs -->

Demographics {data-navmenu="Cluster Level Data" data-navmenu-icon="fa-cogs"}
================================================================================


Unscheduled Care {data-navmenu="Cluster Level Data"}
================================================================================


Outpatient Appointments {data-navmenu="Cluster Level Data"}
================================================================================


Prescribing {data-navmenu="Cluster Level Data"}
================================================================================


National Therapeutic Indicators {data-navmenu="Cluster Level Data"}
================================================================================

<!-- Practice Level Tabs -->

Demographics {data-navmenu="Practice Level Data" data-navmenu-icon="fa-cog"}
================================================================================


Unscheduled Care {data-navmenu="Practice Level Data"}
================================================================================


Outpatient Appointments {data-navmenu="Practice Level Data"}
================================================================================


Prescribing {data-navmenu="Practice Level Data"}
================================================================================


National Therapeutic Indicators {data-navmenu="Practice Level Data"}
================================================================================

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```

