---
title: "GP Cluster Profiles"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    css: phs_style.css
---

```{r setup, include=FALSE}
library(flexdashboard)
library(crosstalk)
library(tidyverse)
library(plotly)
library(phsstyles)

clust <- filter(for_clust, geography_type != "GP Practice")
prac <- filter(for_clust, geography_type == "GP Practice")

pal_clust <- phs_colors(c("phs-purple", "phs-magenta", "phs-blue", "phs-green"))
names(pal_clust) <-  unique(clust$geography_name)

# times = 5 allows up to 18 practices (3 colours, 5 line types)
pal_prac <- rep(phs_colours(rep(c("phs-teal", "phs-liberty", "phs-rust"), times = 6)))
# extract out only what is needed for the practice in the data set
pal_prac <- pal_prac[1:length(unique(prac$geography_name[prac$geography_type == "GP Practice"]))]
names(pal_prac) <- as.character(unique(prac$geography_name[prac$geography_type == "GP Practice"]))

pal_prac <- c(pal_prac, pal_clust)

linetype_prac <- rep(c("solid", "dot", "dash", "longdash", "dashdot", "longdashdot"), each = 3)
linetype_prac <- linetype_prac[1:length(unique(prac$geography_name[prac$geography_type == "GP Practice"]))]
names(linetype_prac) <- unique(prac$geography_name[prac$geography_type == "GP Practice"])

linetype_clust <- rep("solid", 4)
names(linetype_clust) <- unique(clust$geography_name)

linetype_prac <- c(linetype_prac, linetype_clust)

```

Information {data-icon="fa-info-circle"}
================================================================================

We could put some high level summaries on this page (e.g. biggest changes since last year, or biggest difference to HSCP - although note that for some clusters in Lothian they compare to HB since cluster is essentially just the HSCP).

Notes could either go on this page, or could go on a separate "Notes" Page.

<!-- Cluster Level Tabs -->



Demographics {data-navmenu="Cluster Level Data" data-navmenu-icon="fa-cogs"}
================================================================================


Unscheduled Care {data-navmenu="Cluster Level Data"}
================================================================================

sidebar {.sidebar}
--------------------------------------------------------------------------------

```{r create shared data for filters}
unsched_clust <- filter(clust, domain %in% c("A & E", "ACUTE", "OOH")) %>% 
  distinct(geography_name, age_band, indicator, quarter, .keep_all = TRUE) %>% 
  mutate(age_band = factor(age_band, levels = c("All Ages", "Under 65", "65+"))) %>% 
  arrange(age_band, quarter)
unsched_clust <- SharedData$new(unsched_clust)

```

```{r crosstalk filters}
crosstalk::filter_select(
    id = "Indicator",
    label = "Indicator",
    sharedData = unsched_clust,
    group = ~indicator,
    multiple = FALSE
  )

crosstalk::filter_select(
    id = "Age",
    label = "Age",
    sharedData = unsched_clust,
    group = ~age_band,
    #selected="All Ages",
    multiple = FALSE
  )
crosstalk::filter_checkbox(
  id = "Areas",
  label = "Choose areas to compare",
  sharedData = unsched_clust,
  group = ~geography_name
)

# crosstalk::filter_slider(
#   "Financial Year", 
#   "Financial Year", 
#   fy_shared, 
#   ~`Financial Year`, 
#   width = "100%")

```

```{js}
function filter_default(){
  document.getElementById("Age").getElementsByClassName("selectized")[0].selectize.setValue("All Ages",false)
  document.getElementById("Age").getElementsByClassName("selectized")[0].selectize.removeOption("");
  document.getElementById("Indicator").getElementsByClassName("selectized")[0].selectize.setValue("Att Rate Per 1000 Pop",false)
  document.getElementById("Indicator").getElementsByClassName("selectized")[0].selectize.removeOption("");
}

$(document).ready(filter_default);
```

Row
--------------------------------------------------------------------------------

### Trend

```{r}
plot_ly(unsched_clust, 
        x = ~quarter, 
        y = ~rate, 
        color = ~ geography_name, 
        colors = pal_clust,
        mode = "lines+markers")
```

Outpatient Appointments {data-navmenu="Cluster Level Data"}
================================================================================


Prescribing {data-navmenu="Cluster Level Data"}
================================================================================


National Therapeutic Indicators {data-navmenu="Cluster Level Data"}
================================================================================

<!-- Practice Level Tabs -->

Demographics {data-navmenu="Practice Level Data" data-navmenu-icon="fa-cog"}
================================================================================


Unscheduled Care {data-navmenu="Practice Level Data"}
================================================================================

sidebar {.sidebar}
--------------------------------------------------------------------------------

```{r}

unsched_prac <- filter(for_clust, domain %in% c("A & E", "ACUTE", "OOH")) %>% 
  distinct(geography_name, age_band, indicator, quarter, .keep_all = TRUE) %>% 
  mutate(age_band = factor(age_band, levels = c("All Ages", "Under 65", "65+"))) %>% 
  arrange(age_band, quarter)
unsched_prac <- SharedData$new(unsched_prac)
```

```{r}
crosstalk::filter_select(
    id = "Indicator_unsched_prac",
    label = "Indicator",
    sharedData = unsched_prac,
    group = ~indicator,
    multiple = FALSE
  )

crosstalk::filter_select(
    id = "Age_unsched_prac",
    label = "Age",
    sharedData = unsched_prac,
    group = ~age_band,
    #selected="All Ages",
    multiple = FALSE
  )
crosstalk::filter_checkbox(
  id = "Areas_unsched_prac",
  label = "Choose areas to compare",
  sharedData = unsched_prac,
  group = ~geography_name
)

# crosstalk::filter_slider(
#   "Financial Year", 
#   "Financial Year", 
#   fy_shared, 
#   ~`Financial Year`, 
#   width = "100%")

```

```{js}
function filter_default(){
  document.getElementById("Age_unsched_prac").getElementsByClassName("selectized")[0].selectize.setValue("All Ages",false);
  document.getElementById("Age_unsched_prac").getElementsByClassName("selectized")[0].selectize.removeOption("");
  document.getElementById("Indicator_unsched_prac").getElementsByClassName("selectized")[0].selectize.setValue("Att Rate Per 1000 Pop",false);
  document.getElementById("Indicator_unsched_prac").getElementsByClassName("selectized")[0].selectize.removeOption("");
  document.getElementById("Areas_unsched_prac").getElementsByClassName("selectized")[0].selectize.setValue("NHS Scotland",false);
}

$(document).ready(filter_default);
```

Row
--------------------------------------------------------------------------------

### Trend

```{r}
plot_ly(unsched_prac, 
        x = ~quarter, 
        y = ~rate, 
        color = ~ geography_name, 
        colors = pal_prac,
        linetype = ~ geography_name,
        linetypes = linetype_prac,
        mode = "lines+markers")


```


Outpatient Appointments {data-navmenu="Practice Level Data"}
================================================================================


Prescribing {data-navmenu="Practice Level Data"}
================================================================================


National Therapeutic Indicators {data-navmenu="Practice Level Data"}
================================================================================

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```

